Reconciler: A Workflow for Certifying Computational Research Reproducibility

### 2020-05-29 paper/ms.tex
fix arxiv id

We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reconciler-a-workflow-for-certifying-computational-research-reproducibility}} of the Reconciler, that certifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/9999.99999}}.
We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.

>>>>

We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reconciler-a-workflow-for-certifying-computational-research-reproducibility}} of the Reconciler, that certifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}.
We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.
